### 2025-12-29 thesis/evaluation/index.tex
Cleanup

where $\Pi_m$ is the set of valid column permutations (those preserving column
value sets), $\pi(R_g)$ applies permutation $\pi$ to reorder columns in each
row of $R_g$, $\equiv_{\text{multiset}}$ denotes multiset equality (allowing
row reordering) and $ordered(q_g)$ is determining if the ground truth query
$q_g$ contains an \texttt{ORDER BY} clause. Row and value comparisons use
tolerance-based equality for floating-point values ($|\cdot| < 10^{-5}$). The
calculation for measuring \textsc{Natural}'s EA was ported from \textsc{Spider}
\citep{Spider}.

@@

% TODO:
% - End-to-end latency (time from NL query to SQL result)
% - Per-component latency (σ, φ, π, ρ, ν timings)
% - Throughput (queries per second)
% - Resource utilization (GPU memory, CPU usage)

@@

\textcolor{red}{X} external baselines are referenced from previous research:

% - GPT-4 results from literature
% - DIN-SQL, DAIL-SQL, C3 results
% - Other relevant open-source approaches
% - Note: Direct comparison constraints (different models, hardware)

@@

\paragraph{Quantitative Comparison}
% TODO: Create comprehensive comparison table
% - Table: System vs GPT-4, DIN-SQL, DAIL-SQL, C3, etc.
% - Both Spider and Bird results
% - Note differences in model architecture and hardware

>>>>

where $\Pi_m$ is the set of valid column permutations (those preserving column
value sets), $\pi(R_g)$ applies permutation $\pi$ to reorder columns in each
row of $R_g$, $\equiv_{\text{multiset}}$ denotes multiset equality (allowing
row reordering) and $ordered(q_g)$ is determining if the ground truth query
$q_g$ contains an \texttt{ORDER BY} clause.

@@

% TODO:
% - End-to-end latency (time from NL query to SQL result)
% - Per-component latency (σ, φ, π, ρ, ν timings)
% - Resource utilization (GPU memory, CPU usage)

@@

Two primary external baselines are taking into account:

\begin{enumerate}
    \item \textbf{GPT-4} — A proprietary baseline for advanced model
        capabilities without finetuning.
    \item \textbf{OmniSQL} — The open source baseline model series used by
        \textsc{Natural}.
\end{enumerate}

@@

\paragraph{Quantitative Comparison}

% TODO: Create comprehensive comparison table
% - Table: System vs GPT-4, DIN-SQL, DAIL-SQL, C3, etc.
% - Both Spider and Bird results
% - Note differences in model architecture and hardware
